### 2012-02-06 docs/getting_started/getting_started.tex
update for the new directory structure

In MAESTRO, each problem gets their own sub-directory under {\tt
MAESTRO/}.  This sub-directory will contain any problem-specific files
as well as the {\tt GNUmakefile} that specifies how to build the executable.
Note: we rely on features of GNU {\tt make}.  Full details of the
{\tt GNUmakefile} can be found in \S~\ref{sec:adding_problems}.  Here
we will configure for a serial build.

Change directory to {\tt MAESTRO/test2/}.    
We only need to worry about the options at the very top of the
{\tt GNUmakefile} for now.  These should be set as follows:
\begin{itemize}
\item {\tt NDEBUG := t}

@@

\begin{verbatim}
cp ../../extern/EOS/helmeos/helm_table.dat .
\end{verbatim}

>>>>

In \maestro, each problem lives under one of three sub-directories of
{\tt MAESTRO/}: {\tt SCIENCE/}, {\tt TEST\_PROBLEMS/}, or {\tt
UNIT\_TESTS/}.  This problem sub-directory will contain any
problem-specific files as well as the {\tt GNUmakefile} that specifies
how to build the executable.  Note: we rely on features of GNU {\tt
make}.  Full details of the {\tt GNUmakefile} can be found
in \S~\ref{sec:adding_problems}.  Here we will configure for a serial
build.

Change directory to {\tt MAESTRO/TEST\_PROBLEMS/test2/}.    
We only need to worry about the options at the very top of the
{\tt GNUmakefile} for now.  These should be set as follows:
\begin{itemize}
\item {\tt NDEBUG := t}

@@

\begin{verbatim}
cp ../../../extern/EOS/helmeos/helm_table.dat .
\end{verbatim}
